---
title: "Historical horse population in Canada"
bibliography: references.bib
params:
    province: "British Columbia"
output: 
   html_document:
        toc: true
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), '..', 'index.html')) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
```

# Aim
This project explores the historical population of horses in Canada between 1906 and 1972 for each Province.
## Data
```{r load data, include = FALSE}
horse_pop <- read_csv("../data/00030067-eng.csv")
horse_pop <- filter(horse_pop,
                    DATE == "At June 1 (x 1,000)",
                    GEO != "Canada")
horse_pop$Value <- horse_pop$Value * 1000
```
Horse population data were sourced from the [Government of Canada's Open Data website](http://open.canada.ca/en/open-data). Specifically, these two sources were used:
- [Horses, number on farms at June 1 and at December 1](http://open.canada.ca/data/en/dataset/43b3a9b3-3842-45e7-8bc8-c4c27b9462ab)
- [Horses, number on farms at June 1, farm value per head and total farm value](http://open.canada.ca/data/en/dataset/b374f60b-9580-44dc-83f6-c0a850c15f30)
## Methods
@@ -54,14 +55,15 @@

Next we look at the range of the number horses for each provinces at any time point between 1940 - 1972:

```{r max horse table}
max_horses <- horse_pop %>% 
  select(GEO, Value) %>% 
  rename(Province = GEO) %>% 
  group_by(Province) %>% 
  summarize(Maximum = max(Value),
            Minimum = min(Value))
max_horses
kable(max_horses, 
      caption = "Table 1. Maximum and minimum number of horses for each province between 1940 - 1972")
```

Below we zoom in and look at the province of Alberta:



